\thetitle

### 2018-01-19 TeX/manuscript.tex
added three new subsections

    General artificial intelligence refers to machine intelligence than performs a task as successfully as a human does.

@@

@@

\caption{A simple piecewise function modelled by a router network}

@@

The above network models a piecewise function of the expressions $x + y$ and $x *y$, where $x$ and $y$ are inputs. A typical neural network which uses weighted sums and sigmoid activation functions would require many neurons and considerable training to model this function.

>>>>

		General artificial intelligence refers to machine intelligence that performs a task as successfully as a human does.

@@

	\subsection{What is an Artificial Neural Network?}

		An Artificial Neural Network is a computational system of interconnected units, called neurons, such that signals may pass indirectly from a group of neurons, called input neurons, to another group of neurons, called output neurons. The connections between neurons often involve weights, which modify the value of the signal before passing it to the next neuron. Each weight can be adjusted (either manually or via some training algorithm) such that possible input values will yield corresponding desired output values.

@@

		\caption{A simple piecewise function modeled by a router network}

@@

	The above network models a piecewise function of the expressions $x + y$ and $x * y$, where $x$ and $y$ are inputs. A typical neural network which uses weighted sums and sigmoid activation functions would require many neurons and considerable training to model this function.

	\subsection{Networks that are aware of the functions they compute}

		Neural Networks are typically tasked with modeling some relationship between input values and output values. For instance, a Network may be trained to return an output which classifies an input image. However, the extent to which Neural Networks can manipulate their own internal state has not been considered. In this subsection we will attempt to construct a network which can activate some identifiable signal depending on whether or not a function was applied to an input signal or not.

		In the previous subsection, a 'router' was used to decide which function should be used to combine two input values. We will construct a network which imitates the role of the router, using a standard combination of weights and activation functions.

	\subsection{Manipulating symbols}

		Within the standard model of Neural Networks (neurons with activation functions that are interconnected by weights), manipulation of numerical values is commonplace. Manipulation of symbols, on the other hand. In the context of ANN's, a symbol is an internal state of some group of neurons. For example, when processing an input of an image, some neurons may compute a larger activation value if some feature exists in the input, so the region of inputs that corresponds to the existence of the feature 'symbolizes' that feature. Symbols are a useful construct for identifying the underlying meaning behind each computation in a Neural Network.

	\subsection{Can a Neural Network function as Universal Turing Machine?}
